---
title: 'MSB1015: Scientific Programming- Assignment 3 Parallel Computing'
author: "Lian Laudy"
date: "19 oktober 2018"
output: html_document
---

# Load packages

To make sure rcdk function has enough memory, we can increase the heap space with an extra `options()` command. Make
sure the amount of heap space you allocate is not larger than the amount of physical memory your machine has (`4g` is 4 GB, which will be fine if your machine has 8 GB of memory):
```{r}
options(java.parameters = "-Xmx4g")
```

Check if the required packages are already installed. If not, install them:
```{r, echo = FALSE}
packages = c("iterators", "rcdk", "doParallel")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
```

Load the required packages:
```{r}
# the package 'iterators' is used for proper nextElem() support
library(iterators)
library(rcdk)
library(doParallel)
```

# Import data

Import the Structure Data File (SDF) (aid624202.sdf file) using an iterating reader to go through every molecule one by one and add it to a list of molecules
```{r}
# import the .sdf file
iter = iload.molecules('C:/Users/Lian/Desktop/CloudStation/MSB1015 Scientific Programming/Assignments/3 Parallel Computing/aid624202.sdf', type='sdf')

# number of molecules that will be imported
import_mol = 2000

# create an empty list in which the molecules will stored
mols = list()

# generate a progress bar  
pb = txtProgressBar(min = 0, max = import_mol, style = 3)

# define a counter
count = 0

while(hasNext(iter)) {
  # increase count with one
  count = count + 1
  
  # store selected molecule in the list
  mols[[count]] = nextElem(iter)   
  
  # update pogress bar
  setTxtProgressBar(pb, count)
  

  if (count == import_mol) {
    break
  }
}
close(pb)
```
# Compute molecular descriptors in parallel 

```{r}
# detect the number of the computer's cores
num_cores = detectCores() - 1

# create an array of the names of descriptors that will be calculated
desc_names = unique(unlist(sapply(get.desc.categories()[2:4], get.desc.names)))

# generate a progress bar
pb = txtProgressBar(min = 0, max = num_cores, style = 3)

# the molecules are converted into smiles using the get.smiles function
mol_smiles = lapply(unlist(mols),get.smiles)

# create a list that will store the number of seconds that each calculation takes
time = list()

# using a for-loop, the calculation of molecular descriptors is performed using various numbers of cores. The duration of that each calculation takes will be stored
for(i in 1:num_cores){
  
  # generate a cluster
  cl = makeCluster(i)
  
  # descriptor names and molecule smiles are exported to each core
  clusterExport(cl,"desc_names") 
  clusterExport(cl,"mol_smiles")
  
  # load the required packages to each core
  clusterEvalQ(cl, library(rcdk, parallel))
  registerDoParallel(cl) 
  time[i] = system.time(foreach(x=1:import_mol,.combine=rbind) %dopar% eval.desc(parse.smiles(mol_smiles[[x]]),desc_names))
  setTxtProgressBar(pb, i)
  stopCluster(cl)
}
```

# Result
```{r}
plot(unlist(time),xlab="Number of cores",ylab="Time [s]",main=paste0("Duration to calculate descriptors of ",n," molecules"),type='b')
```
