---
title: 'MSB1015: Scientific Programming- Assignment 3 Parallel Computing'
author: "Lian Laudy"
date: "18 oktober 2018"
output: html_document
---

# Load packages

To make sure `rcdk` has enough memory, we can increase the heap space with an extra `options()` command. Make
sure the amount of heap space you allocate is not larger than the amount of physical memory your machine has (`4g` is 4 GB, which will be fine if your machine has 8 GB of memory):
```{r}
options(java.parameters = "-Xmx4g")
```

Check if the required packages are already installed. If not, install them:
```{r, echo = FALSE}
packages = c("iterators", "rcdk", "doParallel")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
```

Load the required packages:
```{r}
# the package 'iterators' is used for proper nextElem() support
library(iterators)
library(rcdk)
library(doParallel)

# Import data
Import the Structure Data File (SDF) (aid624202.sdf file) using an iterating reader to go through every molecule one by one and add it to a list of molecules
```{r}
# import the .sdf file
iter = iload.molecules('C:/Users/Lian/Desktop/CloudStation/MSB1015 Scientific Programming/Assignments/3 Parallel Computing/aid624202.sdf', type='sdf')
